---
title: "`r params$title`"
subtitle: "`r params$subtitle`"
author: "`r params$author`"
date: "`r format(Sys.Date(), '%d.%m.%Y')`"
output:
  xaringan::moon_reader:
    css: ["default", "default-fonts", "style.css"]
    nature:
      ratio: "16:9"
      highlightLines: true
      countIncrementalSlides: false
params:
  title: "Data Analysis using R"
  subtitle: "Introduction"
  author: "Sven Werenbeck-Ueding"
  path_bib: "references.bib"
  path_assets: "../../resources/assets/"
  path_data: "../../data/"
---

<!-- Setup -->

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(fontawesome)
library(DiagrammeR)
library(RefManageR)

# Theming
xaringanExtra::use_panelset()
xaringanExtra::use_tile_view() # Press o for overview in browser

# Bibliography
BibOptions(
  check.entries = FALSE,
  bib.style = "authoryear",
  style = "markdown"
)

bib <- ReadBib(params$path_bib, check = FALSE)
```

```{r eval=TRUE, child = params$path_slides}
```

```{r pdf, include = FALSE, eval=TRUE}
source("https://git.io/xaringan2pdf")
xaringan_to_pdf(
  input = "introduction.html",
  output_file = "introduction.pdf"
)
```

## About This Course

- This course gives practical insights into conducting data analysis projects using R

- Covers data analysis process from beginning to end:
  
  1. Importing and cleaning raw data
  
  2. Exploratory data analysis and visualization
  
  3. Formulating the empirical model
  
  4. Communicating the results

--

.pull-left.short-width[
.big-emoji[`r emo::ji("right arrow")`]
]

.pull-right.lo-wi[
#### All within `R`!
]

---

## Learning Outcomes

By the end of the semester, you will...

--

.right[... be able to conduct empirical projects on your own]

--

.right[... have a solid understanding of R and frequently used packages]

--

.right[... be able to use GitHub for version control of your code and collaboration]

--

.right[... be able to create dynamic, technical reports using Quarto]

---

## Course Structure

--

.pull-left[
#### Lecture

- Class times: Wednesday, 14:00 &ndash; 18:00, GD 03/354

- First half of the semester

- Each lecture covers a different topic

- Topics are shown using practical examples
]

--

.pull-right[
#### Assignment

- Second half of the semester

- Working on an own data analysis project
  
  - In groups of 2 or 3 students
  
  - Submission of course work on **30.01.2024**
  
  - Presentation of results on **31.01.2024**
  
- Code repository and presentation count equally towards the final grade
]

---

## Lecture: Agenda

.pull-left[

| Lecture | Topic             |
|:-------:|:------------------|
| 1       | [R Basics](https://data-analysis-using-r.netlify.app/lecture_htmls/r_basics) |
| 2       | [Version Control](https://data-analysis-using-r.netlify.app/lecture_htmls/version_control) |
| 3       | [Programming](https://data-analysis-using-r.netlify.app/lecture_htmls/programming) |
| 4       | [Importing](https://data-analysis-using-r.netlify.app/lecture_htmls/importing) |
| 5       | [Data Wrangling](https://data-analysis-using-r.netlify.app/lecture_htmls/wrangling) |
| 6       | [Visualization](https://data-analysis-using-r.netlify.app/lecture_htmls/visaulization) |
| 7       | [Modeling](https://data-analysis-using-r.netlify.app/lecture_htmls/modeling) |
| 8       | [Reporting](https://data-analysis-using-r.netlify.app/lecture_htmls/reporting) |

]

.pull-right[

```{r echo=FALSE, out.height="50%"}

grViz(
  '
  digraph {
    fontname="Helvetica,Arial,sans-serif"
	node [fontname="Helvetica,Arial,sans-serif"]
	edge [fontname="Helvetica,Arial,sans-serif"]
    
    rankdir=LR
    
    subgraph cluster_0 {
        style = rounded
        color = black
    
        {
            node [style = rounded, shape = box]
            Import -> Tidy
        }
    
        subgraph cluster_1 {
            style = rounded
            color = black
            
            node [style = rounded, shape = box]
            Transform Visualize Model
            
            edge []
            Transform -> Visualize
            Visualize -> Model
            Model -> Transform
            
            label = "Exploration"
            labeljust = "l"
            labelloc = "b"
        }
    
        {
            node [style = rounded, shape = box]
            Communicate
        }
    
        Tidy -> Transform
        Model -> Communicate [ltail = cluster_1]
        
        label = "Programming"
        labeljust = "l"
        labelloc = "b"
    }
  }
  '
)

```

.right[*Source:* `r Citet(bib, "r4ds")`]

]

---

## Main Literature

`r NoCite(bib, "r4ds")`

`r NoCite(bib, "advancedr")`

```{r, results='asis', echo=FALSE}
PrintBibliography(bib)
```

---

## Organization

- All lecture materials can be found on the course website: <https://data-analysis-using-r.netlify.app/>

- Registration via Flexnow required!
  
  - Registration period: **24.10.2023** to **07.11.2023**
  
  - *Note:* Registration has to be done before the group work starts
  
- Use the Moodle forum to form groups of 2 to 3 students yourselves

--

- After the registration period and when all groups are formed, the data will be provided to you via [sciebo](https://hochschulcloud.nrw/)

  - Cloud service with 30GB storage

  - Register via your RUB-mail (or any other mail from a higher education institution in NRW)
  
  - A folder containing the data will be shared with you
  
--
  
.pull-left.short-width[
.big-emoji[`r emo::ji("warning")`]
]

.pull-right.lo-wi[
#### **Do not store this data anywhere else than your own sciebo folder!**
]

---

## Contact Information
  
  - Mail: [sven.werenbeck-ueding@ruhr-uni-bochum.de](mailto:sven.werenbeck-ueding@ruhr-uni-bochum.de)
  
  - Office: GD 03/367
  
  - Office hours: Please make an appointment via [email](mailto:sven.werenbeck-ueding@ruhr-uni-bochum.de) in advance
