---
title: "`r params$title`"
subtitle: "`r params$subtitle`"
author: "`r params$author`"
date: "`r format(Sys.Date(), '%d.%m.%Y')`"
output:
  xaringan::moon_reader:
    css: ["default", "default-fonts", "style.css"]
    nature:
      ratio: "16:9"
      highlightLines: true
      countIncrementalSlides: false
params:
  title: "Data Analysis using R"
  subtitle: "Assignment"
  author: "Sven Werenbeck-Ueding"
  path_bib: "references.bib"
  path_assets: "../../resources/assets/"
  path_data: "../../data/"
---

<!-- Setup -->

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(fontawesome)
library(DiagrammeR)
library(RefManageR)
library(kableExtra)

# Theming
xaringanExtra::use_panelset()
xaringanExtra::use_tile_view() # Press o for overview in browser

# Bibliography
BibOptions(
  check.entries = FALSE,
  bib.style = "authoryear",
  style = "markdown"
)

bib <- ReadBib(params$path_bib, check = FALSE)
```

```{r eval=TRUE, child = params$path_slides}
```

```{r pdf, include = FALSE, eval=FALSE}
source("https://git.io/xaringan2pdf")
xaringan_to_pdf(
  input = "introduction.html",
  output_file = "introduction.pdf"
)
```

## Course Work

- For this course, you are tasked with conducting your empirical research in groups of 2 to 3 students

- You will be creating your own GitHub repository where you will collaborate with your group members

- The repository has to be submitted until 30.01.2024 and the results have to be presented on 31.01.2024

- Code repository and presentation count equally towards the final grade

- You will be analyzing real-world data provided by the RWI &ndash; Leibniz Institute for Economic Research and the North Rhine-Westphalia Ministry of Schools and Education

---

## Timeline

| Date                          |   |
|-------------------------------|---|
| 24.10.2023 &ndash; 07.11.2023 | Register via Flexnow<br/><br/>Form groups of 2 to 3 students (use the Moodle forum) |
| today &ndash; 08.11.2023      | Register on sciebo: https://hochschulcloud.nrw/<br/><br/>Send an email to [sven.werenbeck-ueding@rub.de](mailto:sven.werenbeck-ueding@ruhr-uni-bochum.de) containing the members of your group with name, student ID and the email with which they registered on sciebo |
| 09.11.2023                    | Copy the data from the shared sciebo folder to your own folder in sciebo and start working on your project by creating a GitHub repository dedicated to your project<br/><br/>Add the GitHub user "swerenbeck" (that's me) as a collaborator to your GitHub repository |
| 30.01.2024                    | Create a feature branch labelled "submission" to submit your repository and also submit your repository as a ZIP archive via email to [sven.werenbeck-ueding@rub.de](mailto:sven.werenbeck-ueding@ruhr-uni-bochum.de) |
| 31.01.2024                    | Present your results in class |

---

## Assignment: Housing Prices and School Quality

- Large number of studies find significant willingness-to-pay for living near better-performing schools, see e. g. the meta study by `r Citet(bib, "m11")`

  - School performance usually measured through average test scores
  
  - (Elementary) schools in the neighborhood are a deciding factor for parents when buying a home
  
  - Parents pay a mark-up to live near "better" schools with a good learning environment for their child `r emo::ji("right arrow")` reflected in higher prices for these homes
  
--

- In North Rhine-Westphalia, schools are assigned a school social index reflecting the social composition of a school's student body

  - A bad score indicates that a school is confronted with severe challenges
  
  - Might indicate a less favorable learning environment for a child
  
  - Similar to the above example with average test scores, parents would likely choose to buy a home near schools with a better social school index `r emo::ji("right arrow")` should be reflected in higher house/apartment prices

---

## School Social Index in NRW

- The School Social Index is a school-specific social index for general public education schools (primary schools, secondary schools, i. e. *Hauptschule* and *Realschule*, comprehensive schools and grammar schools)

- The index ranging from 1 (good) to 9 (bad) reflects the social composition of a school's student body and is taken into account in the distribution of resources

--

- The social composition of the pupils in the schools is mapped via the following four indicators:

  1. Children and youth poverty: The social space indicator used is based on the density of the SGB II rate of minors in the estimated catchment area of primary schools.

  2. Share of pupils with predominantly German family language

  3. Share of pupils with migration background (first-generation immigrants)

  4. Share of pupils with special needs (focus: learning, emotional and social development, speaking)
  
--

*Note:* More information can be found [here](https://www.schulministerium.nrw/sozialindex) (unfortunately, only in German... `r emo::ji("face with rolling eyes")`)

---

## School Social Index in NRW

```{r echo=FALSE}
tribble(
  ~ "School type", ~ "1", ~ "2", ~ "3", ~ "4", ~ "5", ~ "6", ~ "7", ~ "8", ~ "9", ~ "w/o index",
  "Elementary school", 644, 823, 529, 300, 175, 145, 70, 14, 4, 8,
  "Secondary school (Hauptschule)", 1, 7, 25, 40, 35, 32, 27, 7, 4, 1,
  "Secondary school (Realschule)", 48, 95, 104, 53, 25, 3, 3, NA, NA, 1,
  "Secondary school", 4, 44, 36, 11, 5, 2, NA, NA, NA, 5,
  "Comprehensive school", 30, 129, 91, 39, 9, 7, 2, NA, NA, 11,
  "Grammar school", 260, 186, 45, 10, 1, 1, 1, NA, NA, NA,
) %>% 
  mutate(
    Sum = rowSums(across(where(is.numeric), ~ .), na.rm = T),
    across(everything(), as.character),
    across(everything(), ~ ifelse(is.na(.), "-", .))
  ) %>% 
  kbl(align = c("l", rep("r", 11))) %>% 
  add_header_above(c(" " = 1, "School social index" = 10, " " = 1)) %>% 
  pack_rows(
    index = c("Primary education" = 1, "Secondary education" = 5),
    bold = F, italic = T
  ) %>% 
  footnote("School social indexes were calculated on the basis of the Official School Data 2018/2019. The data was taken from: https://www.schulministerium.nrw/sozialindex (last accessed on 03.10.2023).")

```

---

## Valuing Amenities: Hedonic Pricing

...

---

## Your Task

...

---

## Housing Data

- The *Research Data Center Ruhr* (FDZ Ruhr) publishes on a regular basis all residential properties advertised on the internet platform *ImmobilienScout24* that are offered for sale or rent

- Datasets provide detailed information on housing attributes and location of these properties

- You will be provided access to a campus file containing all advertisements from 2022

#### Citation:

RWI and ImmobilienScout24 (2023). RWI Real Estate Data - Campus File Cross-Section. Version: 1. RWI &ndash; Leibniz Institute for Economic Research. Dataset. [doi.org/10.7807/immo:red:cross:v4](https://doi.org/10.7807/immo:red:cross:v4)

---

## School Data

The provided data on schools contains the following data sets:

- `school_data.csv`: Basic information on all schools in NRW

  - School type
  - Legal form
  - ZIP code area
  - District
  - ...

- `2022_social_index.csv`: Social school indexes per school for the year 2022

- `number_pupils.xlsx`: Number of pupils/students per school

- `keys.xlsx`: Labels for the keys `legal_form`, `district`, `school_operation` and `school_type` in the `school_data.csv` data set

*Note:* The data was taken from the North Rhine-Westphalia Ministry of Schools and Education (https://www.schulministerium.nrw/open-data, last accessed on 03.10.2023)

---

## Data Access

After the registration period and when all groups are formed, the data will be provided to you via [sciebo](https://hochschulcloud.nrw/):

- Cloud service with 30GB storage

- Register via your RUB-mail (or any other mail from a higher education institution in NRW)
  
- A folder containing the data will be shared with you

--

.pull-left.short-width[
.big-emoji[`r emo::ji("warning")`]
]

.pull-right.lo-wi[
#### **Don't store the data anywhere else than sciebo!**
]

---

## Code Repository

- GitHub repository containing **all** code and results

- Collaborate in the repository with your group members

- Use the features provided by GitHub:
  
  - Split your analysis in reasonable subtasks using GitHub issues
  
  - Work on feature branches to complete the tasks
  
  - Make use of commits and commit messages
  
  - Use pull requests to review each other's code

- Follow the guidelines stated in the lecture(s)

--

.pull-left.short-width[
.big-emoji[`r emo::ji("warning")`]
]

.pull-right.lo-wi[
#### **Do not push the provided data to your code repository!**
]

---

## Presentation

- **15 min. presentation** followed by a **5 min. discussion**

- Every group member has to contribute to the presentation to equal parts

- Has to be created using [Quarto](https://quarto.org/) and submitted as PDF

- Should give insights on

  - Motivation, research question and contribution to the existing literature
  
  - Data used and empirical strategy
  
  - Main findings
  
  - Limitations of your approach
  
---

## General Remarks on Presentation Structure

--

#### Introduction

  - Introduce and motivate your topic
  - What is your research question?
  - What are the main findings of the related literature and how does your research contribute to it?

--

#### Data and Empirical Strategy

  - What data do you use and how did you pre-process it? Were some observations omitted? If so, why?
  - Which empirical strategy do you use to answer your research question? And why this approach?

--

#### Results

  - What are the main findings?
  - Are there heterogeneous effects?

--

#### Conclusion

  - Summarize your findings and set them in the context of the existing literature
  - State the limitations of your approach

---

## Submission

**Deadline: 30.01.2024**

.pull-left[
#### Code Repository

- GitHub repository for collaboration with your group members and containing **all** code and results of your group work (including the presentation as PDF)

- Add "swerenbeck" (that's me) as a collaborator

- Create a feature branch labelled "submission" which will be graded
]

.pull-right[
#### Email

- One email per group to [sven.werenbeck-ueding@rub.de](mailto:sven.werenbeck-ueding@rub.de)

- Attach the whole repository from the feature branch "submission" as a ZIP archive and the presentation as PDF

- To create a ZIP archive right-click with your mouse on the repository folder on your local machine and select "In ZIP-Datei komprimieren" / "Compress to ZIP file"
]

---

# References

```{r, results='asis', echo=FALSE}
PrintBibliography(bib)
```
