---
title: "`r params$title`"
subtitle: "`r params$subtitle`"
author: "`r params$author`"
date: "`r format(Sys.Date(), '%d.%m.%Y')`"
output:
  xaringan::moon_reader:
    css: ["default", "default-fonts", "style.css"]
    nature:
      ratio: "16:9"
      highlightLines: true
      countIncrementalSlides: false
params:
  title: "Data Analysis using R"
  subtitle: "Introduction & Assignment"
  author: "Sven Werenbeck-Ueding"
  path_bib: "references.bib"
  path_assets: "../../resources/assets/"
  path_data: "../../data/"
---

<!-- Setup -->

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(fontawesome)
library(DiagrammeR)
library(RefManageR)
library(kableExtra)
library(sf)

# Theming
xaringanExtra::use_panelset()
xaringanExtra::use_tile_view() # Press o for overview in browser

# Bibliography
BibOptions(
  check.entries = FALSE,
  bib.style = "authoryear",
  style = "markdown"
)

bib <- ReadBib(params$path_bib, check = FALSE)
```

```{r eval=TRUE, child = params$path_slides}
```

```{r pdf, include = FALSE, eval=TRUE}
source("https://git.io/xaringan2pdf")
xaringan_to_pdf(
  input = "intro_assignment.html",
  output_file = "intro_assignment.pdf"
)
```

## About This Course

- This course gives practical insights into conducting data analysis projects using R

- Covers data analysis process from beginning to end:
  
  1. Importing and cleaning raw data
  
  2. Exploratory data analysis and visualization
  
  3. Formulating the empirical model
  
  4. Communicating the results

--

.pull-left.short-width[
.big-emoji[`r emo::ji("right arrow")`]
]

.pull-right.lo-wi[
#### All within `R`!
]

---

## Learning Outcomes

By the end of the semester, you will...

--

.right[... be able to conduct empirical projects on your own]

--

.right[... have a solid understanding of R and frequently used packages]

--

.right[... be able to use GitHub for version control of your code and collaboration]

--

.right[... be able to create dynamic, technical reports using Quarto]

---

## Course Structure

--

.pull-left[
#### Lecture

- Class times: Wednesday, 14:00 &ndash; 18:00, GD 03/354

- First half of the semester

- Each lecture covers a different topic

- Topics are shown using practical examples
]

--

.pull-right[
#### Assignment

- Second half of the semester

- Working on an own data analysis project
  
  - In groups of 2 or 3 students
  
  - Submission of course work on **30.01.2024**
  
  - Presentation of results on **31.01.2024**
  
- Code repository and presentation count equally towards the final grade
]

---

## Lecture: Agenda

.pull-left[

| Lecture | Topic             |
|:-------:|:------------------|
| 1       | [R Basics](https://data-analysis-using-r.netlify.app/lecture_htmls/r_basics) |
| 2       | [Version Control](https://data-analysis-using-r.netlify.app/lecture_htmls/version_control) |
| 3       | [Programming](https://data-analysis-using-r.netlify.app/lecture_htmls/programming) |
| 4       | [Importing](https://data-analysis-using-r.netlify.app/lecture_htmls/importing) |
| 5       | [Data Wrangling](https://data-analysis-using-r.netlify.app/lecture_htmls/wrangling) |
| 6       | [Visualization](https://data-analysis-using-r.netlify.app/lecture_htmls/visaulization) |
| 7       | [Modeling](https://data-analysis-using-r.netlify.app/lecture_htmls/modeling) |
| 8       | [Reporting](https://data-analysis-using-r.netlify.app/lecture_htmls/reporting) |

]

.pull-right[

```{r echo=FALSE, out.height="50%"}

grViz(
  '
  digraph {
    fontname="Helvetica,Arial,sans-serif"
	node [fontname="Helvetica,Arial,sans-serif"]
	edge [fontname="Helvetica,Arial,sans-serif"]
    
    rankdir=LR
    
    subgraph cluster_0 {
        style = rounded
        color = black
    
        {
            node [style = rounded, shape = box]
            Import -> Tidy
        }
    
        subgraph cluster_1 {
            style = rounded
            color = black
            
            node [style = rounded, shape = box]
            Transform Visualize Model
            
            edge []
            Transform -> Visualize
            Visualize -> Model
            Model -> Transform
            
            label = "Exploration"
            labeljust = "l"
            labelloc = "b"
        }
    
        {
            node [style = rounded, shape = box]
            Communicate
        }
    
        Tidy -> Transform
        Model -> Communicate [ltail = cluster_1]
        
        label = "Programming"
        labeljust = "l"
        labelloc = "b"
    }
  }
  '
)

```

.right[*Source:* `r Citet(bib, "r4ds")`]

]

---

## Main Literature

`r NoCite(bib, "r4ds")`

`r NoCite(bib, "advancedr")`

```{r, results='asis', echo=FALSE}
PrintBibliography(bib, start = 1, end = 2)
```

---

## Contact Information

- Mail: [sven.werenbeck-ueding@ruhr-uni-bochum.de](mailto:sven.werenbeck-ueding@ruhr-uni-bochum.de)
  
- Office: GD 03/367
  
- Office hours: Please make an appointment via [email](mailto:sven.werenbeck-ueding@ruhr-uni-bochum.de) in advance

---

class: middle

# The Assignment

---

## Housing Prices and School Quality

- Large number of studies find significant willingness-to-pay for living near better-performing schools, see e. g. the meta study by `r Citet(bib, "m11")`

  - School performance usually measured through average test scores
  
  - (Elementary) schools in the neighborhood are a deciding factor for parents when buying a home
  
- Parents pay a mark-up to live near "better" schools with a good learning environment for their child

- Having good schools nearby can be understood as a local amenity

--

.pull-left.short-width[
.big-emoji[`r emo::ji("right arrow")`]
]

.pull-right.lo-wi[
Reflected in higher prices for homes located near "better" schools
]

---

## Valuing Amenities: Hedonic Prices

> [...] model of product differentiation based on the hedonic hypothesis that goods are valued for their utility-bearing attributes or characteristics.
>
> .right[`r Citet(bib, "r78")`]

--

Price for some complex good is defined by a function of its $K$ characteristics, $p(x)=p(x_1,\dots,x_k,\dots,x_K)$, such that the price for characteristic $k$ is the first-order derivative: $\frac{\partial p(x)}{\partial x_k}=p_k(z)$

--

.pull-left.short-width[
.big-emoji[`r emo::ji("right arrow")`]
]

.pull-right.lo-wi[
Under general equilibrium assumptions, implicit prices of non-market goods (e. g. living near a good school) are revealed through product differentiation of complex goods (e. g. housing)
]

--

.pull-left.short-width[
.big-emoji[`r emo::ji("right arrow")`]
]

.pull-right.lo-wi[
If two houses differ in one characteristic only, the difference in their prices is attributable to this characteristic
]

---

## Hedonic Price Function

Hedonic price functions are usually estimated using a log-linear functional form:

$$\ln p_{itr}=S_{it}\beta+N_{it}\gamma+\tau_t+\rho_r+\varepsilon_{it}$$

- $p_{itr}$: Price of dwelling $i$ at time $t$ in region $r$

- $S_{it}$: Vector of structural characteristics of dwelling $i$ at time $t$, e. g. the number of rooms

- $N_{it}$: Vector of neighborhood characteristics of dwelling $i$ at time $t$

- $\tau_t$: Time fixed effects for time $t$

- $\rho_r$: Region fixed effects for region $r$

- $\varepsilon_{it}\sim N(0,\sigma^2)$

--

.pull-left.short-width[
.big-emoji[`r emo::ji("right arrow")`]
]

.pull-right.lo-wi[
$\hat{\beta}$ and $\hat{\gamma}$ give a vectors of estimated implicit prices for structural and neighborhood characteristics under the c. p. condition
]

---

## School Quality in NRW

- In North Rhine-Westphalia, schools are assigned a school social index reflecting the social composition of a school's student body

  - A bad score indicates that a school is confronted with severe challenges
  
  - Might indicate a less favorable learning environment for a child
  
  - Schools with bad scores are allocated more resources
  
  - Bad learning environment probably outweighs the additional resources
  
- Similar to the example with average test scores, parents would likely choose to buy a home near schools with a better social school index

--

.pull-left.short-width[
.big-emoji[`r emo::ji("right arrow")`]
]

.pull-right.lo-wi[
Neighborhoods with "better" schools may attract more parents, resulting in higher prices for houses/apartments
]

---

## School Social Index in NRW

- School-specific social index for general public education schools (primary schools, secondary schools, i. e. *Hauptschule*, *Realschule* and *Sekundarschule*, comprehensive schools and grammar schools)

- The index ranging from 1 (good) to 9 (bad) reflects the social composition of a school's student body and is taken into account in the distribution of resources

--

- The social composition of the pupils in the schools is mapped via the following four indicators:

  1. Children and youth poverty

  2. Share of pupils with predominantly Non-German speaking households

  3. Share of pupils with migration background (first-generation immigrants)

  4. Share of pupils with special needs (focus: learning, emotional and social development, speaking)
  
--

*Note:* More information can be found [here](https://www.schulministerium.nrw/sozialindex) (unfortunately, only in German... `r emo::ji("face with rolling eyes")`)

---

## School Social Index in NRW

```{r echo=FALSE}
tribble(
  ~ "School type", ~ "1", ~ "2", ~ "3", ~ "4", ~ "5", ~ "6", ~ "7", ~ "8", ~ "9", ~ "w/o index",
  "Elementary school", 644, 823, 529, 300, 175, 145, 70, 14, 4, 8,
  "Secondary school (Hauptschule)", 1, 7, 25, 40, 35, 32, 27, 7, 4, 1,
  "Secondary school (Realschule)", 48, 95, 104, 53, 25, 3, 3, NA, NA, 1,
  "Secondary school", 4, 44, 36, 11, 5, 2, NA, NA, NA, 5,
  "Comprehensive school", 30, 129, 91, 39, 9, 7, 2, NA, NA, 11,
  "Grammar school", 260, 186, 45, 10, 1, 1, 1, NA, NA, NA,
) %>% 
  mutate(
    Sum = rowSums(across(where(is.numeric), ~ .), na.rm = T),
    across(everything(), as.character),
    across(everything(), ~ ifelse(is.na(.), "-", .))
  ) %>% 
  kbl(align = c("l", rep("r", 11))) %>% 
  add_header_above(c(" " = 1, "School social index" = 10, " " = 1)) %>% 
  pack_rows(
    index = c("Primary education" = 1, "Secondary education" = 5),
    bold = F, italic = T
  ) %>% 
  footnote("School social indexes were calculated on the basis of the Official School Data 2018/2019. The data was taken from: https://www.schulministerium.nrw/sozialindex (last accessed on 03.10.2023).")

```

---

## School Social Index in NRW

```{r include=FALSE}
sf <- "SSI_per_AGS.geojson" %>% 
  st_read() %>% 
  filter(!is.na(mean_SSI))
```

.center[
```{r echo=FALSE, message=FALSE, warning=FALSE}
sf %>% 
  ggplot() +
  geom_sf(aes(fill = mean_SSI)) +
  labs(
    fill = "SSI",
    caption = unname(latex2exp::TeX("\\textit{Note:} SSI were averaged over elementary schools of municipalities."))
  ) +
  scale_fill_gradientn(colors = c("#9DBF9E", "#FCB97D", "#A84268")) +
  theme_minimal() +
  theme(
    axis.title = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    plot.caption = element_text(size = 15, hjust = 0),
    legend.title = element_text(size = 15)
  )
```
]


---

## Your Task

- Develop a specific and narrow research question revolving around housing prices and school quality in groups of 2 to 3 students

- Prepare the provided data to your needs

  - Online advertisements from *Immobilienscout24* containing houses and apartments offered for sale and apartments offered for rent in 2022
  
  - School social index from NRW's Ministry of Schools and Education
  
  - Further data you consider relevant for your research question (the database of the [Federal Statistical Office of Germany](https://www-genesis.destatis.de/genesis/online?operation=sprachwechsel&language=en#abreadcrumb) or the regional database [INKAR](https://www.inkar.de/))

- Formulate an empirical strategy designed to answer your research question

- Develop your code and collaborate in a GitHub repository

- Present your results in class at the end of the semester

- Code repository and presentation count equally towards the final grade

---

## Timeline

| Date                          |   |
|-------------------------------|---|
| 24.10.2023 &ndash; 07.11.2023 | Register via Flexnow<br/><br/>Form groups of 2 to 3 students (use the Moodle forum) |
| today &ndash; 08.11.2023      | Register on sciebo: https://hochschulcloud.nrw/<br/><br/>Send an email to [sven.werenbeck-ueding@rub.de](mailto:sven.werenbeck-ueding@ruhr-uni-bochum.de) containing the members of your group with name, student ID and the email with which they registered on sciebo |
| 09.11.2023                    | Copy the data from the shared sciebo folder to your own folder in sciebo and start working on your project by creating a GitHub repository dedicated to your project<br/><br/>Add the GitHub user "swerenbeck" (that's me) as a collaborator to your GitHub repository |
| 30.01.2024                    | Create a feature branch labelled "submission" to submit your repository and also submit your repository as a ZIP archive via email to [sven.werenbeck-ueding@rub.de](mailto:sven.werenbeck-ueding@ruhr-uni-bochum.de) |
| 31.01.2024                    | Present your results in class |

---

## Code Repository

- GitHub repository containing **all** code and results

- Collaborate in the repository with your group members

- Use the features provided by GitHub:
  
  - Split your analysis in reasonable subtasks using GitHub issues
  
  - Work on feature branches to complete the tasks
  
  - Make use of commits and commit messages
  
  - Use pull requests to review each other's code

- Follow the guidelines stated in the lecture(s)

--

.pull-left.short-width[
.big-emoji[`r emo::ji("warning")`]
]

.pull-right.lo-wi[
#### **Do not push the provided data to your code repository!**
]

---

## Presentation

- **15 min. presentation** followed by a **5 min. discussion**

- Every group member has to contribute to the presentation to equal parts

- Has to be created using [Quarto](https://quarto.org/) and submitted as PDF

- Should give insights on

  - Motivation, research question and contribution to the existing literature
  
  - Data used and empirical strategy
  
  - Main findings
  
  - Limitations of your approach
  
---

## General Remarks on the Presentation

--

#### Introduction

  - Introduce and motivate your topic
  - What is your research question?
  - What are the main findings of the related literature and how does your research contribute to it?

--

#### Data and Empirical Strategy

  - What data do you use and how did you pre-process it? Were some observations omitted? If so, why?
  - Which empirical strategy do you use to answer your research question? And why this approach?

--

#### Results

  - What are the main findings?
  - Are there heterogeneous effects?

--

#### Conclusion

  - Summarize your findings and set them in the context of the existing literature
  - State the limitations of your approach

---

## Submission

**Deadline: 30.01.2024**

.pull-left[
#### Code Repository

- GitHub repository for collaboration with your group members and containing **all** code and results of your group work (including the presentation as PDF)

- Add "swerenbeck" (that's me) as a collaborator

- Create a feature branch labelled "submission" which will be graded
]

.pull-right[
#### Email

- One email per group to [sven.werenbeck-ueding@rub.de](mailto:sven.werenbeck-ueding@rub.de)

- Attach the whole repository from the feature branch "submission" as a ZIP archive and the presentation as PDF

- To create a ZIP archive right-click with your mouse on the repository folder on your local machine and select "In ZIP-Datei komprimieren" / "Compress to ZIP file"
]

---

class: middle

# The Data

---

## Housing Data

- The *Research Data Center Ruhr* (FDZ Ruhr) publishes on a regular basis all residential properties advertised on the internet platform *ImmobilienScout24* that are offered for sale or rent

- Datasets provide detailed information on housing attributes and location of these properties

- You will be provided access to a campus file containing all advertisements from 2022

#### Citation:

RWI and ImmobilienScout24 (2023). RWI Real Estate Data - Campus File Cross-Section. Version: 1. RWI &ndash; Leibniz Institute for Economic Research. Dataset. [doi.org/10.7807/immo:red:cross:v4](https://doi.org/10.7807/immo:red:cross:v4)

---

## School Data

The provided data on schools contains the following data sets:

- `school_data.csv`: Basic information on all schools in NRW

  - School type
  - Legal form
  - ZIP code area
  - District
  - ...

- `2022_social_index.csv`: Social school indexes per school for the year 2022

- `number_pupils.xlsx`: Number of pupils/students per school

- `keys.xlsx`: Labels for the keys `legal_form`, `district`, `school_operation` and `school_type` in the `school_data.csv` data set

- `plz_AGS.csv`: Mapping between ZIP codes and the AGS (*Allgemeinder Gemeindeschlüssel*, municipality code)

*Note:* The data was taken from the North Rhine-Westphalia Ministry of Schools and Education (https://www.schulministerium.nrw/open-data, last accessed on 03.10.2023)

---

## Regional Data

- The data set `region_data.csv` contains demographics on municipality-level in NRW (*Gemeinde*):

  - `munic_name`, `AGS`: Name and code of the municipality

  - `population`: Population count
  
  - `work_age_population`: Working age population count (16 to 65 years old)
  
  - `unemployed`: Number of unemployed
  
  - `low_income_hh`, `middle_income_hh`, `high_income_hh`: Share of low (< 1.500€ per month), middle (between 1.500€ and 3.600€ per month) and high (> 3.600€ per month) income households
  
  - `population_density`: Population density (inhabitants per $km^2$)
  
  - `migrants`: Number of migrants
  
  - `region_type`: Region type, i. e. urban (metropolitan), urban (regiopolitan), rural (close to city region) or rural (peripheral)
  
*Note:* The number of migrants was taken from the regional database of the [Federal Statistical Office](https://www.regionalstatistik.de/genesis/online/logon) and is based on the 2011 census and the rest of the data was obtained from [INKAR](https://www.inkar.de/) is from 31.12.2020

---

## Data Access

After the registration period and when all groups are formed, the data will be provided to you via [sciebo](https://hochschulcloud.nrw/):

- Cloud service with 30GB storage

- Register via your RUB-mail (or any other mail from a higher education institution in NRW)
  
- A folder containing the data will be shared with you

--

.pull-left.short-width[
.big-emoji[`r emo::ji("warning")`]
]

.pull-right.lo-wi[
#### **Do not store the data anywhere else than sciebo!**
]

---

layout: true

## Some Limitations

---

Not controlling for socio-economic indicators will confound your estimates for the implicit prices of school quality since both are correlated

--

`r emo::ji("warning")` Regions with high unemployment, share of migrants etc. will have higher SSI scores

`r emo::ji("warning")` These indicators are not available to you on the lowest regional aggregation level of schools (ZIP code areas)

`r emo::ji("warning")` You may not be able to control for the location of a dwelling inside a region

---

You will have to use the SSI on an aggregate level on which you can also control for the socio-economic indicators to entangle the effect of a region's average school quality from its local economic condition, such that $$\ln p_{itr}=S_{it}\beta+N_{r}\gamma+\tau_t+\rho_r+\varepsilon_{it},$$ where $N_r$ are region-specific SSI and socio-economic indicators.

--

.pull-left.short-width[
.big-emoji[`r emo::ji("warning")`]
]

.pull-right.lo-wi[
Your analysis will still suffer from omitted variable bias as you can not control for the location of a dwelling inside a region (and thus its actual distance to the nearest school)
]

---

layout: false

# References

```{r, results='asis', echo=FALSE}
PrintBibliography(bib)
```
